Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-02 doc/PRF2022/PRF_main.tex
latest changes; added figure 2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representation and time stepping}
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretize each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the first kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\sigma$ is a scalar-valued
density function. The subscript in $\dif s_\yy$ denotes integration with
respect to $\yy \in \Gamma$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx), \quad
    \xx \in \Gamma.
\end{align}

@@

We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP
surface.  Then, the boundary condition (BC) can be classified into three
categories: $\min g = 0$, $\min g >0$, and $\min g <0$.  These three
categories correspond to three characteristic values of $b$ in
\eqref{eq:bc-type}: $b=1$, $b=2$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics
of 198 particles and 60 particles in a quiescent flow as shown in
Figure~\ref{fig:relax}. Three distinct configurations emerge: (i)
bilayer for $b = 1$, (ii) multilamellar for $b = 2$, and (iii) striated
for $b = 0$.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}
  \todo[inline]{We should capitalize bc is that it reads BC like we have
  in the text.}
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy~\eqref{eq:free_energy} decreases
  in the mobility problem formulation. The initial energies are for the
  configuration in Figure~\ref{fig:relax}(a) and the final energies are
  for the near-equilibrium configurations shown in
  Figures~\ref{fig:relax}(b)--(d). The solid curves are the energies for
  the $N_b=60$ cases and the dashed curves are the energies for the $N_b
  = 198$ cases normalized by $60/198$, showing that the energy
  approximately scales with the number of particles.  Panel (b) shows
  the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs.
  The curve styles are identical those in panel (a). The
  near-equilibrium configurations depend on the initial configurations
  and the results show that for both $N_b=60$ and $N_b=198$ cases,
  bilayer and multi-lamellar configurations have similar trends in
  orientational parameters. The results of the striated configuration,
  however, depend on the initial geometrical setup.}
\end{figure}

@@

Finally, we use the scalar order parameter for orientational order:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta$ is a circular mean defined as the orientation of the
largest eigenvalue of $\dd_1\dd_1^\top + \cdots +
\dd_{N_b}\dd_{N_b}^\top$. A value $S_2(t) = 1$ indicates that all
particle directors lie on a common axis e.g., two parallel vectors with
possibly opposite direction are ordered. A value far from 1 indicates
disorder.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
  the configurations with streamlines of a vesicle is in a TG flow at
  $t=1 \upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the enclosed
  area $A_0/A$ calculated from the bilayer midplane decreases over time
  and the total length (shown in the inset) measured from the midplane
  remains nearly constant with small magnitude of oscillations.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representations}
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretize each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the first kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\sigma$ is a scalar-valued
density function. The subscript in $\dif s_\yy$ denotes integration with
respect to $\yy \in \Gamma$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx), \quad
    \xx \in \Gamma.
\end{align}

@@

We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP
surface.  Then, the boundary condition (BC) can be classified into three
categories: $\min g(\xx) = 0$, $\min g(\xx) >0$, and $\min g(\xx) <0$
where the extrema are taken for $\xx \in \Gamma_i$.  These three
categories correspond to three characteristic values of $b$ in
\eqref{eq:bc-type}: $b=1$, $b=2$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics
of 198 particles and 60 particles in a quiescent flow as shown in
Figure~\ref{fig:relax}. Three distinct configurations emerge: (i)
bilayer for $b = 1$, (ii) multilamellar for $b = 2$, and (iii) striated
for $b = 0$.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy~\eqref{eq:free_energy} decreases
  in the mobility problem formulation. The initial energies are for the
  configuration in Figure~\ref{fig:relax}(a) and the final energies are
  for the near-equilibrium configurations shown in
  Figures~\ref{fig:relax}(b)--(d). The solid curves are the energies for
  the $N_b=60$ cases and the dashed curves are the energies for the $N_b
  = 198$ cases normalized by $60/198$, showing that the energy
  approximately scales with the number of particles.  Panel (b) shows
  the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs.
  The curve styles are identical those in panel (a). The
  near-equilibrium configurations depend on the initial configurations
  and the results show that for both $N_b=60$ and $N_b=198$ cases,
  bilayer and multi-lamellar configurations have similar trends in
  orientational parameters. The results of the striated configuration,
  however, depend on the initial geometrical setup.}
\end{figure}

@@

Finally, we use the scalar order parameter for orientational order:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta$ is a circular mean defined as the orientation of the
principal eigenvector of the matrix $\dd_1\dd_1^\top + \cdots +
\dd_{N_b}\dd_{N_b}^\top$. A value $S_2(t) = 1$ indicates that all
particle directors lie on a common axis e.g., two parallel vectors with
possibly opposite direction are ordered. A value far from 1 indicates
disorder.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
  the configurations with streamlines of a vesicle is in a TG flow at
  $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the relative enclosed
  area $A/A_0$ calculated from the bilayer midplane decreases over time.
  The inset shows the relative length $l/l_0$ 
  which remains nearly constant with small magnitude of oscillations
  The inset and main panel have the same  horizontal axis.}
\end{figure}
